Computing solution space properties by generic programming tensor networks \thanks{\funding{...}}

### 2022-03-21 paper/paper.tex
Updates from Overleaf

    \includegraphics[width=\textwidth, trim={0.0cm 0cm 0.0cm 0cm}, clip]{figures/fig6.pdf}

@@

This appendix covers some technical aspects of this paper, including an open source package and a gist about how to implement this package. If you are only interested in using, please checking our GitHub repository for an efficient and full featured implementation aimed for productively:
\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
\begin{lstlisting}
pkg> add GraphTensorNetworks
\end{lstlisting}

>>>>

    \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{figures/fig6.pdf}

@@

This appendix covers some technical aspects of this paper, including an open source package and a gist about how to implement this package. If you are only interested in using, please checking our GitHub repository for an efficient and full featured implementation aimed for productively:
\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
\begin{lstlisting}
pkg> add GraphTensorNetworks
\end{lstlisting}
To use it, just open Julia REPL and type

\begin{lstlisting}
julia> using GraphTensorNetworks, Graphs

julia> solve(
           IndependentSet(
               Graphs.random_regular_graph(20, 3);
               optimizer = TreeSA()
           ),
           GraphPolynomial()
       )
0-dimensional Array{Polynomial{BigInt, :x}, 0}:
Polynomial(1 + 20*x + 160*x^2 + 659*x^3 + 1500*x^4 + 1883*x^5 + 1223*x^6 + 347*x^7 + 25*x^8)
\end{lstlisting}

The first time you run the code might trigger the just in time compiling,
it will be a bit slow, but the following computing will be fast.
